How do expert pianists adapt their didactic demonstration to novices' skill levels?

### 2022-11-02 paper/manuscript.Rmd
update discussion
Signed-off-by: Atsuko Tominaga <Tominaga_Atsuko@phd.ceu.edu>

---
title             : "The title"
shorttitle        : "Title"

@@

abstract: |
  AAA

keywords          : "keywords"
wordcount         : "X"

#bibliography      : ""

@@

One of the limitation of the current study is that . One solution would be to create a model performance where both articulation and dynamics was implemented and ask participants (expert pianists) to listen to it. After they had an idea of what the model performance (i.e., the goal of the performance) is, they have a chance to listen to the recordings produced by students with various skill levels as we did in the current experiment.

we found that even during measuring the baseline performance before the experiment, many participants tend to implement some articulation even though nothing was notated on the sheet music (see details: Supplementary Material). To make the implementation of articulation clear, we particularly selected detached performances for the recordings where articulation was missing. Another possibility is that dynamics implementation was not perceived by participants, therefore they did not modulate the dynamic-related aspect of performances for teaching.

One of the limitations of the current study is that ---.

Future research should investigate.

Limitation

>>>>

---
title             : "How do expert pianists adapt their didactic demonstration to novices’ skill levels?"
shorttitle        : "How do expert pianists adapt their didactic demonstration to novices’ skill levels?"

@@

abstract: |
  Later

keywords          : "keywords"

bibliography      : "references.bib"

@@

One of the limitations of the current study is that participants did not have an idea about what the ideal performance was. As some participants reported that "(students had) very different interpretations of the melody" or "all kids played rhythmically correct" in the questionnaire, it is plausible that the lack of articulation and/or dynamics might not have been perceived as errors. One solution would be to create a model performance where both articulation and dynamics was implemented and ask participants (expert pianists) to listen to it before starting the current experiment so that they can detect errors in the recordings.

The reason why participants considered different recording variations as interpretations rather than errors might stem from the fact that all the recordings did not include any pitch errors and performed the piece with the stable tempo. This was to make sure that we manipulated articulation and dynamics features of the recordings only. However, all the recordings might not have sounded like unskillful students were playing. In order to create more realistic unskillful performances, it might be useful to add some jitters to the tempo of the recordings we created, or to ask unskillful students to play the piece and extract the temporal feature of their performances.

Evidence from infant-directed action research has shown that caregivers are sensitive to the infants' skill levels and modified their demonstration according to infants' abilities to perform a motor task [@fukuyama_2015]. In the current experiment, expert pianists needed to perform in the absence of actual students. Future research should investigate how expert pianists and students dynamically interact in a situation where they can communicate as a naturalistic lesson and examine how the performance of expert pianists and that of students are related.

### 2022-11-02 paper/manuscript.tex
update discussion
Signed-off-by: Atsuko Tominaga <Tominaga_Atsuko@phd.ceu.edu>

% Options for packages loaded elsewhere
\PassOptionsToPackage{unicode}{hyperref}
\PassOptionsToPackage{hyphens}{url}
%
\documentclass[
  man]{apa6}
\usepackage{amsmath,amssymb}
\usepackage{lmodern}
\usepackage{iftex}
\ifPDFTeX
  \usepackage[T1]{fontenc}
  \usepackage[utf8]{inputenc}
  \usepackage{textcomp} % provide euro and other symbols
\else % if luatex or xetex
  \usepackage{unicode-math}
  \defaultfontfeatures{Scale=MatchLowercase}
  \defaultfontfeatures[\rmfamily]{Ligatures=TeX,Scale=1}
\fi
% Use upquote if available, for straight quotes in verbatim environments
\IfFileExists{upquote.sty}{\usepackage{upquote}}{}
\IfFileExists{microtype.sty}{% use microtype if available
  \usepackage[]{microtype}
  \UseMicrotypeSet[protrusion]{basicmath} % disable protrusion for tt fonts
}{}
\makeatletter
\@ifundefined{KOMAClassName}{% if non-KOMA class
  \IfFileExists{parskip.sty}{%
    \usepackage{parskip}
  }{% else
    \setlength{\parindent}{0pt}
    \setlength{\parskip}{6pt plus 2pt minus 1pt}}
}{% if KOMA class
  \KOMAoptions{parskip=half}}
\makeatother
\usepackage{xcolor}
\usepackage{graphicx}
\makeatletter
\def\maxwidth{\ifdim\Gin@nat@width>\linewidth\linewidth\else\Gin@nat@width\fi}
\def\maxheight{\ifdim\Gin@nat@height>\textheight\textheight\else\Gin@nat@height\fi}
\makeatother
% Scale images if necessary, so that they will not overflow the page
% margins by default, and it is still possible to overwrite the defaults
% using explicit options in \includegraphics[width, height, ...]{}
\setkeys{Gin}{width=\maxwidth,height=\maxheight,keepaspectratio}
% Set default figure placement to htbp
\makeatletter
\def\fps@figure{htbp}
\makeatother
\setlength{\emergencystretch}{3em} % prevent overfull lines
\providecommand{\tightlist}{%
  \setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}
\setcounter{secnumdepth}{-\maxdimen} % remove section numbering
% Make \paragraph and \subparagraph free-standing
\ifx\paragraph\undefined\else
  \let\oldparagraph\paragraph
  \renewcommand{\paragraph}[1]{\oldparagraph{#1}\mbox{}}
\fi
\ifx\subparagraph\undefined\else
  \let\oldsubparagraph\subparagraph
  \renewcommand{\subparagraph}[1]{\oldsubparagraph{#1}\mbox{}}
\fi
\ifLuaTeX
\usepackage[bidi=basic]{babel}
\else
\usepackage[bidi=default]{babel}
\fi
\babelprovide[main,import]{english}
% get rid of language-specific shorthands (see #6817):
\let\LanguageShortHands\languageshorthands
\def\languageshorthands#1{}
% Manuscript styling
\usepackage{upgreek}
\captionsetup{font=singlespacing,justification=justified}

@@

\usepackage{xpatch}
\makeatletter
\xapptocmd\appendix
  {\xapptocmd\section
    {\addcontentsline{toc}{section}{\appendixname\ifoneappendix\else~\theappendix\fi\\: #1}}
    {}{\InnerPatchFailed}%
  }
{}{\PatchFailed}
\keywords{keywords\newline\indent Word count: X}
\DeclareDelayedFloatFlavor{ThreePartTable}{table}
\DeclareDelayedFloatFlavor{lltable}{table}
\DeclareDelayedFloatFlavor*{longtable}{table}
\makeatletter
\renewcommand{\efloat@iwrite}[1]{\immediate\expandafter\protected@write\csname efloat@post#1\endcsname{}}
\makeatother
\usepackage{csquotes}
\ifLuaTeX
  \usepackage{selnolig}  % disable illegal ligatures
\fi
\IfFileExists{bookmark.sty}{\usepackage{bookmark}}{\usepackage{hyperref}}
\IfFileExists{xurl.sty}{\usepackage{xurl}}{} % add URL line breaks if available
\urlstyle{same} % disable monospaced font for URLs
\hypersetup{
  pdftitle={The title},
  pdfauthor={Atsuko Tominaga1, Günther Knoblich1, \& Natalie Sebanz1},
  pdflang={en-EN},
  pdfkeywords={keywords},
  hidelinks,
  pdfcreator={LaTeX via pandoc}}

\title{The title}
\author{Atsuko Tominaga\textsuperscript{1}, Günther Knoblich\textsuperscript{1}, \& Natalie Sebanz\textsuperscript{1}}
\date{}

\shorttitle{Title}

@@

\abstract{%
AAA
}

@@

Overall, the results indicated that expert pianists seemed to prioritise the teaching of articulation. One possibility would be that articulation was more important for the piece we selected or the piece itself naturally invited some implementation of articulation. In our previous experiment, we found that even during measuring the baseline performance before the experiment, many participants tend to implement some articulation even though nothing was notated on the sheet music (see details: Supplementary Material). To make the implementation of articulation clear, we particularly selected detached performances for the recordings where articulation was missing. Another possibility is that dynamics implementation was not perceived by participants, therefore they did not modulate the dynamic-related aspect of performances for teaching.

One of the limitations of the current study is that ---.

Future research should investigate.

Limitation

@@

\hypertarget{acknowledgement}{%
\section{Acknowledgement}\label{acknowledgement}}

>>>>

% Options for packages loaded elsewhere
\PassOptionsToPackage{unicode}{hyperref}
\PassOptionsToPackage{hyphens}{url}
%
\documentclass[
  man]{apa6}
\usepackage{amsmath,amssymb}
\usepackage{lmodern}
\usepackage{iftex}
\ifPDFTeX
  \usepackage[T1]{fontenc}
  \usepackage[utf8]{inputenc}
  \usepackage{textcomp} % provide euro and other symbols
\else % if luatex or xetex
  \usepackage{unicode-math}
  \defaultfontfeatures{Scale=MatchLowercase}
  \defaultfontfeatures[\rmfamily]{Ligatures=TeX,Scale=1}
\fi
% Use upquote if available, for straight quotes in verbatim environments
\IfFileExists{upquote.sty}{\usepackage{upquote}}{}
\IfFileExists{microtype.sty}{% use microtype if available
  \usepackage[]{microtype}
  \UseMicrotypeSet[protrusion]{basicmath} % disable protrusion for tt fonts
}{}
\makeatletter
\@ifundefined{KOMAClassName}{% if non-KOMA class
  \IfFileExists{parskip.sty}{%
    \usepackage{parskip}
  }{% else
    \setlength{\parindent}{0pt}
    \setlength{\parskip}{6pt plus 2pt minus 1pt}}
}{% if KOMA class
  \KOMAoptions{parskip=half}}
\makeatother
\usepackage{xcolor}
\usepackage{graphicx}
\makeatletter
\def\maxwidth{\ifdim\Gin@nat@width>\linewidth\linewidth\else\Gin@nat@width\fi}
\def\maxheight{\ifdim\Gin@nat@height>\textheight\textheight\else\Gin@nat@height\fi}
\makeatother
% Scale images if necessary, so that they will not overflow the page
% margins by default, and it is still possible to overwrite the defaults
% using explicit options in \includegraphics[width, height, ...]{}
\setkeys{Gin}{width=\maxwidth,height=\maxheight,keepaspectratio}
% Set default figure placement to htbp
\makeatletter
\def\fps@figure{htbp}
\makeatother
\setlength{\emergencystretch}{3em} % prevent overfull lines
\providecommand{\tightlist}{%
  \setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}
\setcounter{secnumdepth}{-\maxdimen} % remove section numbering
% Make \paragraph and \subparagraph free-standing
\ifx\paragraph\undefined\else
  \let\oldparagraph\paragraph
  \renewcommand{\paragraph}[1]{\oldparagraph{#1}\mbox{}}
\fi
\ifx\subparagraph\undefined\else
  \let\oldsubparagraph\subparagraph
  \renewcommand{\subparagraph}[1]{\oldsubparagraph{#1}\mbox{}}
\fi
\newlength{\cslhangindent}
\setlength{\cslhangindent}{1.5em}
\newlength{\csllabelwidth}
\setlength{\csllabelwidth}{3em}
\newlength{\cslentryspacingunit} % times entry-spacing
\setlength{\cslentryspacingunit}{\parskip}
\newenvironment{CSLReferences}[2] % #1 hanging-ident, #2 entry spacing
 {% don't indent paragraphs
  \setlength{\parindent}{0pt}
  % turn on hanging indent if param 1 is 1
  \ifodd #1
  \let\oldpar\par
  \def\par{\hangindent=\cslhangindent\oldpar}
  \fi
  % set entry spacing
  \setlength{\parskip}{#2\cslentryspacingunit}
 }%
 {}
\usepackage{calc}
\newcommand{\CSLBlock}[1]{#1\hfill\break}
\newcommand{\CSLLeftMargin}[1]{\parbox[t]{\csllabelwidth}{#1}}
\newcommand{\CSLRightInline}[1]{\parbox[t]{\linewidth - \csllabelwidth}{#1}\break}
\newcommand{\CSLIndent}[1]{\hspace{\cslhangindent}#1}
\ifLuaTeX
\usepackage[bidi=basic]{babel}
\else
\usepackage[bidi=default]{babel}
\fi
\babelprovide[main,import]{english}
% get rid of language-specific shorthands (see #6817):
\let\LanguageShortHands\languageshorthands
\def\languageshorthands#1{}
% Manuscript styling
\usepackage{upgreek}
\captionsetup{font=singlespacing,justification=justified}

@@

\usepackage{xpatch}
\makeatletter
\xapptocmd\appendix
  {\xapptocmd\section
    {\addcontentsline{toc}{section}{\appendixname\ifoneappendix\else~\theappendix\fi\\: #1}}
    {}{\InnerPatchFailed}%
  }
{}{\PatchFailed}
\keywords{keywords}
\DeclareDelayedFloatFlavor{ThreePartTable}{table}
\DeclareDelayedFloatFlavor{lltable}{table}
\DeclareDelayedFloatFlavor*{longtable}{table}
\makeatletter
\renewcommand{\efloat@iwrite}[1]{\immediate\expandafter\protected@write\csname efloat@post#1\endcsname{}}
\makeatother
\usepackage{csquotes}
\ifLuaTeX
  \usepackage{selnolig}  % disable illegal ligatures
\fi
\IfFileExists{bookmark.sty}{\usepackage{bookmark}}{\usepackage{hyperref}}
\IfFileExists{xurl.sty}{\usepackage{xurl}}{} % add URL line breaks if available
\urlstyle{same} % disable monospaced font for URLs
\hypersetup{
  pdftitle={How do expert pianists adapt their didactic demonstration to novices' skill levels?},
  pdfauthor={Atsuko Tominaga1, Günther Knoblich1, \& Natalie Sebanz1},
  pdflang={en-EN},
  pdfkeywords={keywords},
  hidelinks,
  pdfcreator={LaTeX via pandoc}}

\title{How do expert pianists adapt their didactic demonstration to novices' skill levels?}
\author{Atsuko Tominaga\textsuperscript{1}, Günther Knoblich\textsuperscript{1}, \& Natalie Sebanz\textsuperscript{1}}
\date{}

\shorttitle{How do expert pianists adapt their didactic demonstration to novices' skill levels?}

@@

\abstract{%
Later
}

@@

Overall, the results indicated that expert pianists seemed to prioritise the teaching of articulation. One possibility would be that articulation was more important for the piece we selected or the piece itself naturally invited some implementation of articulation. In our previous experiment, we observed most participants implemented articulation (particularly legato) when they were asked to perform the piece even when neither of articulation nor dynamics was notated on the sheet music. Therefore, it is possible that expert pianists were particularly sensitive to the lack of articulation in the recordings and trying to teach it. Another possibility is that dynamics modulations in the recordings were too subtle to be noticed by participants.

One of the limitations of the current study is that participants did not have an idea about what the ideal performance was. As some participants reported that ``(students had) very different interpretations of the melody'' or ``all kids played rhythmically correct'' in the questionnaire, it is plausible that the lack of articulation and/or dynamics might not have been perceived as errors. One solution would be to create a model performance where both articulation and dynamics was implemented and ask participants (expert pianists) to listen to it before starting the current experiment so that they can detect errors in the recordings.

The reason why participants considered different recording variations as interpretations rather than errors might stem from the fact that all the recordings did not include any pitch errors and performed the piece with the stable tempo. This was to make sure that we manipulated articulation and dynamics features of the recordings only. However, all the recordings might not have sounded like unskillful students were playing. In order to create more realistic unskillful performances, it might be useful to add some jitters to the tempo of the recordings we created, or to ask unskillful students to play the piece and extract the temporal feature of their performances.

Evidence from infant-directed action research has shown that caregivers are sensitive to the infants' skill levels and modified their demonstration according to infants' abilities to perform a motor task (Fukuyama et al., 2015). In the current experiment, expert pianists needed to perform in the absence of actual students. Future research should investigate how expert pianists and students dynamically interact in a situation where they can communicate as a naturalistic lesson and examine how the performance of expert pianists and that of students are related.

@@

\hypertarget{acknowledgement}{%
\section*{Acknowledgement}\label{acknowledgement}}
\addcontentsline{toc}{section}{Acknowledgement}

\hypertarget{refs}{}
\begin{CSLReferences}{1}{0}
\leavevmode\vadjust pre{\hypertarget{ref-fukuyama_2015}{}}%
Fukuyama, H., Qin, S., Kanakogi, Y., Nagai, Y., Asada, M., \& Myowa-Yamakoshi, M. (2015). Infant's action skill dynamically modulates parental action demonstration in the dyadic interaction. \emph{Developmental Science}, \emph{18}(6), 1006--1013. \url{https://doi.org/10.1111/desc.12270}

\end{CSLReferences}
